\newpage
\begin{center}
\thispagestyle{empty}
\vspace*{2\baselineskip}
\LARGE{\textbf{ABSTRACT}}\\[0.5cm]
\end{center}
\thispagestyle{empty}
\doublespacing
\begin{normalsize}
Invoice application being the basic need for all business, yet the software required for this purpose needs to be purchased from some software company. This creates the problem if any modifications are need to be brought to taxation methods or if any features needs to be added to meet some requirement.

Generally the invoice applications available today are just offline applications simply storing the billing info in local database. This is a drawback in the era of internet world, where people expect to get all information online regarding their purchasing details, due payments.

All the businesses irrespective of the levels of business either it may be
distributors or retailers who have wide range of customers necessarily
require an elegant and user-friendly invoice application in order for the
smooth conduction of their business. Thereby it becomes a need and
demand for an Invoice Application.

In this Invoice Web Application users first need to create their profile and then can add the items involved in their business along with the details of stocks and prices.

In this project, we have implemented a general purpose invoice web application where any user can create a profile and use it create invoices for their requirement. Since, its a web application all data and information are stored in online database server . It also has the advantage of easy updates if needed.

Whereas customers can obtain their invoices as PDF and can have trustworthy services regarding their due payments.

By the implementation of this Invoice Web Application project we can overcome the drawback of traditional invoice application and we can provide a modern general purpose invoice web application made available for any user to create invoices conveniently.
\\[1cm]
\end{normalsize}