\newpage
\vspace*{1\baselineskip}
\begin{center}
\thispagestyle{empty}
\LARGE{\textbf{ACKNOWLEDGEMENTS}}\\[1cm]
\end{center}
\vspace{0.05cm}
\doublespacing
Salutations to our beloved and highly esteemed institute ``Malnad College Of Engineering" for having well qualified staff and labs furnished with necessary equipment.

The successful completion of any task would be incomplete without mentioning the people who have constantly guided and inspired for the project and the report generation.

We avail this opportunity to thank all those people who have helped us in the whole process of completion of this project and the report.

We would like to express our deepest gratitude to our mentor {\textbf{Prof. Shashidhara H V}},Department of Computer Science and Engineering for his daily evaluation of the work and for providing us constant encouragement with his unflinching support and valuable guidance throughout this project. We are indebted to him as he has considered us worthy of this project and invested his faith in us. It was a great privilege to work under him. We will take away a lot more than just the technical knowledge from him.We would also like to place our special thanks to Dr.C V Venkatesh, Principal,Dr Geetha Kiran A,HOD Computer science and Engineering department and all Panel members Mr. Shashidhara H V(Panel Head),Associate Professor, Mr.Keerthi K S,Assistant Professor, Mr.Vasanth Kumar N.T,Assistant Professor and Mr.Ravi Kumar D,Assistant Professor,Malnad College of Engineering for providing the opportunity and the facilities for the completion of our project.\\

\large{\hspace*{3.5in} Hariharan K(4MC19CS050)}\\
\large{\hspace*{3.7in} Dhyan S Agni(4MC19CS043)}\\
\large{\hspace*{2.8in} Chirag K Deshbhandari(4MC19CS035)}\\

% Salutations to our beloved and highly esteemed institute ``Malnad College Of Engineering" for having well qualified staff and labs furnished with necessary equipment.

% The successful completion of any task would be incomplete without mentioning the people who have constantly guided and inspired for the project and the report generation.

% We avail this opportunity to thank all those people who have helped us in the whole process of completion of this project and the report.

% We would like to express our deepest gratitude to our mentor Mr. Shashidhara H V, Department of Computer Science \& Engineering for his daily evaluation of the work and for providing us constant encouragement with his unflinching support and valuable guidance throughout this project. We are indebted to him as he has considered us worthy of this project and invested his faith in us. It was a great privilege to work under him. We will take away a lot more than just the technical knowledge from him.

% We would also like to place our special thanks to Dr. C V Venkatesh, Principal, Malnad College Of Engineering for providing the opportunity and the facilities for the completion of our project. \\
\newpage
