\chapter{Conclusion and Future Works}

\section{Conclusion}
In this project, we have implemented a general-purpose invoice web application, in which any user just by the creation of profile can have a web based invoice application.
Whereas customers can obtain their invoices as PDF and can have trustworthy services regarding their due payments.

Our findings are summarised as follows:
\begin{itemize}
\item Any level of business can now have a functional invoice application for their own company.
\item Invoice history keeps storing the information transaction details and due payments, helpful in proper running of business.
\item Invoices are generated as PDF which avoids traditional way of printing invoices and can transfer these invoice PDF easily to the customers. 
\item Being a web based application has the versatility of easy upgrades of features in the application whenever necessary.
\end{itemize}

\pagebreak

\section{Future Works}
The aim of the project is to overcome the limitations of traditional way of printing paper invoices. Apart from this we would like to improvise our project and consider integration of future implementation of features such as:

\begin{itemize}
\item Customisation Features
\item Customer Side Interface
\end{itemize}
General-purpose application platform requires, the need of satisfying the requirements of various range of users. Scenario where taxation methods may differ from business to business need of different feature requirement. Hence, we think of future implementations regarding the {\textbf{\textit{customisation features}}} in the application in order to satisfy various feature requirements for different set of users.

Integration of {\textbf{\textit{customer side interface}}} will be helpful directly sharing the details of invoices to the customer. Keep track of all their purchases and details regarding their due payments for each invoice. Such a customer-side interface will also be helpful in implementing online payments of their invoices.